Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-03-29 paper/paper.tex
late night comit of the finished additional experiment with fune-tuning

% testing the fx of the threshold
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

% effects of extra training epochs and the impact of tau
We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
the compression and performance metrics before fine-tuning for various threshold levels
on figure~\ref{fig:hist__and__threshold__tradeoff}. From \eqref{eq:elbo_with_coef} and
the relative positions of the compression curves it can be concluded that $C$ has much
more substantial impact on the sparsity and performance, than the choice of $\tau$.
Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
downwards.

% (pending) threshold and fune-tuning?
% By reducing the excess degrees of freedom, high compression rates could act as a regularizer,
% leaving less capacity for overfitting. Which seems sufficient enough for models in higher
% compression regime
% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.

>>>>

% testing the fx of the threshold
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
  \end{subfigure} \\
  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold__fine-tune.pdf}
  \end{subfigure}
  \caption{%
    Performance (smooth curve) and compression (curve with markers) of select experiments
    before (\textit{top}) and after (\textit{bottom}) fine-tuning.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

% effects of extra training epochs and the impact of tau
We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
the compression and performance metrics before fine-tuning for various threshold levels
on figure~\ref{fig:hist__and__threshold__tradeoff} (top). From \eqref{eq:elbo_with_coef} and
the relative positions of the compression curves it can be concluded that $C$ has much
more substantial impact on the sparsity and performance, than the choice of $\tau$.
Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
downwards.

% (pending) threshold and fune-tuning? BETTER text
Bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} show improved performance
for thresholds below $-\tfrac12$ after fine-tuning. For higher $\tau$ the final stage
improves performance of a highly compressed model ($C=0.05$), while leaving moderately
compressed model ($C=0.005$) unaffected. This behaviour can be explained by the regularizing
effect of high compression rates, which servely reduce the excess degrees of freedom,
leaving less capacity for overfitting.
% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel

% takeaway: fine tune seems to improve performance for highly compressed models, but
% within a limit. Worth a try for moderately compressed models, but willl must likely
% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
% sparsity more strongly, than varying $\tau$. But this is only observational.
